---
title: "Tf-Idf anaylsis on historical English corpus"
author: "ChiChen Lo"
date: "`r Sys.Date()`"
---
## Summary  
This markdown code evaluate the subset of the COHA corpus to find out the words used in the last 200 years.
***

### Import all packages needed and read the corpus
```{r, message=FALSE}
library(tm)
library(Matrix)
library(ggplot2)
library(RColorBrewer)
setwd('~/Courses/DSPwithR/DataScienceProgramming2018spring/Project1/')
a = Corpus(DirSource('./COHA/'), readerControl = list(language="lat"))
```

### data cleaning
```{r}
a <- tm_map(a , stripWhitespace)
a <- tm_map(a, tolower)
a <- tm_map(a, stemDocument, language = "english")
```

### get the term-document matrix (weighted with TF-IDF)
```{r}
terms = TermDocumentMatrix(a, control = list(stopwords=stopwords('english'), weighting = function(x) weightTfIdf(x, normalize = TRUE)))
```

### Check the top TF-IDF ranking terms and the distribution of terms and the correspoding TF-IDF
```{r, echo=FALSE}
freq=rowSums(as.matrix(terms))
head(sort(freq, decreasing = T), n=24)
plot(sort(freq, decreasing = T),col="blue",main="TF-IDF frequencies", xlab="rank", ylab = "TF-IDF")
```


### Analysis every 50 years
```{r}
doc_list = Docs(terms)
doc1800 = grep('.*_18[0-4][0-9]_[0-9]*.txt', doc_list, value = TRUE)
doc1850 = grep('.*_18[5-9][0-9]_[0-9]*.txt', doc_list, value = TRUE)
doc1900 = grep('.*_19[0-4][0-9]_[0-9]*.txt', doc_list, value = TRUE)
doc1950 = grep('.*_19[5-9][0-9]_[0-9]*.txt', doc_list, value = TRUE)
doc2000 = grep('.*_20[0-4][0-9]_[0-9]*.txt', doc_list, value = TRUE)
```


### 1800~1849, the top TF-IDF ranked terms
```{r}
subM = terms[, doc1800]
freq = rowSums(as.matrix(subM))
freq1800 = freq
head(sort(freq, decreasing = T), n=24)

high.freq=tail(sort(freq),n=15)
hfp.df=as.data.frame(sort(high.freq))
hfp.df$names <- rownames(hfp.df) 
ggplot(hfp.df, aes(reorder(names,high.freq), high.freq)) +
  geom_bar(stat="identity", fill='blue') + coord_flip() + 
  xlab("Terms") + ylab("TF-IDF") +
  ggtitle("TFIDF-ranked Terms (1800-1849)")
```

### 1850~1899, the top TF-IDF ranked terms
```{r}
subM = terms[, doc1850]
freq = rowSums(as.matrix(subM))
freq1850 = freq
head(sort(freq, decreasing = T), n=24)

high.freq=tail(sort(freq),n=15)
hfp.df=as.data.frame(sort(high.freq))
hfp.df$names <- rownames(hfp.df) 
ggplot(hfp.df, aes(reorder(names,high.freq), high.freq)) +
  geom_bar(stat="identity", fill='Yellow') + coord_flip() + 
  xlab("Terms") + ylab("TF-IDF") +
  ggtitle("TFIDF-ranked Terms (1850-1899)")
```

### 1900~1949, the top TF-IDF ranked terms
```{r}
subM = terms[, doc1900]
freq = rowSums(as.matrix(subM))
freq1900 = freq
head(sort(freq, decreasing = T), n=24)

high.freq=tail(sort(freq),n=15)
hfp.df=as.data.frame(sort(high.freq))
hfp.df$names <- rownames(hfp.df) 
ggplot(hfp.df, aes(reorder(names,high.freq), high.freq)) +
  geom_bar(stat="identity", fill='red') + coord_flip() + 
  xlab("Terms") + ylab("TF-IDF") +
  ggtitle("TFIDF-ranked Terms (1900-1949)")
```

### 1950~1999, the top TF-IDF ranked terms
```{r}
subM = terms[, doc1950]
freq = rowSums(as.matrix(subM))
freq1950 = freq
head(sort(freq, decreasing = T), n=24)

high.freq=tail(sort(freq),n=15)
hfp.df=as.data.frame(sort(high.freq))
hfp.df$names <- rownames(hfp.df) 
ggplot(hfp.df, aes(reorder(names,high.freq), high.freq)) +
  geom_bar(stat="identity", fill='orange') + coord_flip() + 
  xlab("Terms") + ylab("TF-IDF") +
  ggtitle("TFIDF-ranked Terms (1950-1999)")
```

### 2000~2009, the top TF-IDF ranked terms
```{r}
subM = terms[, doc2000]
freq = rowSums(as.matrix(subM))
freq2000 = freq
head(sort(freq, decreasing = T), n=24)

high.freq=tail(sort(freq),n=15)
hfp.df=as.data.frame(sort(high.freq))
hfp.df$names <- rownames(hfp.df) 
ggplot(hfp.df, aes(reorder(names,high.freq), high.freq)) +
  geom_bar(stat="identity", fill='green') + coord_flip() + 
  xlab("Terms") + ylab("TF-IDF") +
  ggtitle("TFIDF-ranked Terms (2000-2009)")
```

### The co-appearaence matrix of top-1000 TF-IDf ranked terms
```{r}
top1800 = attributes(head(sort(freq1800, decreasing=TRUE), n=1000))$names
top1850 = attributes(head(sort(freq1850, decreasing=TRUE), n=1000))$names
top1900 = attributes(head(sort(freq1900, decreasing=TRUE), n=1000))$names
top1950 = attributes(head(sort(freq1950, decreasing=TRUE), n=1000))$names
top2000 = attributes(head(sort(freq2000, decreasing=TRUE), n=1000))$names
totallList = list(top1800, top1850, top1900, top1950, top2000)
list_names <- c("1800~", "1850~", "1900~", "1950~", "2000~")

M = (matrix(nrow = 5, ncol = 5))
for (i in 1:5) {
  for (j in 1:5) {
    M[i,j] <- length(intersect(totallList[[i]], totallList[[j]]))
  }
}
rownames(M) = list_names
colnames(M) = list_names
print(M)
```

Appearently, the far away, the larger the difference usage of word. But it is interesting that the term ranked high in 2000~ are very different than any other time periods. More than 50% difference compared with the word used in 1950-.

### The co-appearaence matrix of top-100 TF-IDf ranked terms
```{r}
top1800 = attributes(head(sort(freq1800, decreasing=TRUE), n=100))$names
top1850 = attributes(head(sort(freq1850, decreasing=TRUE), n=100))$names
top1900 = attributes(head(sort(freq1900, decreasing=TRUE), n=100))$names
top1950 = attributes(head(sort(freq1950, decreasing=TRUE), n=100))$names
top2000 = attributes(head(sort(freq2000, decreasing=TRUE), n=100))$names
totallList = list(top1800, top1850, top1900, top1950, top2000)
list_names <- c("1800~", "1850~", "1900~", "1950~", "2000~")

M = (matrix(nrow = 5, ncol = 5))
for (i in 1:5) {
  for (j in 1:5) {
    M[i,j] <- length(intersect(totallList[[i]], totallList[[j]]))
  }
}
rownames(M) = list_names
colnames(M) = list_names
print(M)
```